Shift-sensitive Power Transformations for Transforming Data to Normality

### 2023-11-03 manuscript/manuscript.Rmd
Work on manuscript.

## Goodness of fit

@@

## Empirical goodness of fit test

To develop an empirical goodness of fit test we need to consider two parameters: the central portion $\kappa$ as a fixed parameter, and test statistic $\tau_{\text{gof}}$. We will first define the central portion $\kappa$.

@@

@@

@@

### Car data

The Top Gear dataset contains data on 297 cars that appeared on the BBC television show *Top Gear*. Fuel consumption contains outliers.

```{r top-gear, warning=FALSE, message=FALSE, fig.cap=cap}
cap <- paste0(
  "Insert caption here"
)

@@

Top gear dataset, weight

### Housing data

>>>>

## Empirical central normality test

@@

## Empirical central normality test

To develop an empirical test for central normality we need to consider two parameters: the central portion $\kappa$ as a fixed parameter, and test statistic $\tau_{\text{gof}}$. We will first define the central portion $\kappa$.

@@

**MISSING TABLE DATA FOR YEO-JOHNSON**

@@

In this section, we assess shift sensitive power transformations using real datasets.

@@

### Top Gear dataset

```{r top-gear, warning=FALSE, message=FALSE, fig.cap=cap, fig.height=2}
cap <- paste0(
  "\\label{fig:top-gear}",
  "Quantile-quantile plots for the fuel consumption data in the Top Gear dataset. ",
  "This data contains three strong outliers for highly efficient vehicles. ",
  "The left panel shows the quantile-quantile plot for the original data. ",
  "The middle panel shows the quantile-quantile plots for data transformed using ",
  "the original Yeo-Johnson transformation, and Raymaekers and Rousseeuw's robust adaptation [@Raymaekers2021-kq]. ",
  "For these, the empirical central normality test yields $p=0.01$, and $p=0.58$, respectively. ",
  "The right panels shows the quantile-quantile plots for data transformed using ",
  "the non-robust and robust shift-sensitive transformations. ",
  "For these, the empirical central normality test yields $p=0.01$, and $p=0.36$, respectively. ",
  "Samples with observed quantiles below $-3.0$ or above $3.0$ are indicated by crosses."
)

@@

The Top Gear dataset contains data on 297 cars that appeared on the BBC television show *Top Gear*. Fuel consumption contains outliers. Figure \ref{fig:top-gear} shows that the outliers cause non-robust transformations to fail to transform the data to a centrally normal distribution (empirical central normality test $p = 0.01$). Robust transformations produce distributions that are centrally normal (empirical central normality test $p > 0.05$).

### Housing dataset

modeldata::Sacramento$price
